---
title: "Multilevel?"
author: "Blain Morin"
output: pdf_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(RSQLite)
library(lubridate)
library(stargazer)

```

* This document looks at differences between territories, contract lengths, and individual CRES providers
* Not a time series buff, but it may be worth noting that the data are hierarchical: we have offers located in different territories. We also have individual trends for each company. 


```{r}

conn = dbConnect(RSQLite::SQLite(), "puco.db")

test = dbGetQuery(conn, "SELECT * FROM Responses WHERE ContractTerms in (3, 12, 24) AND refRateType = 'Fixed' and MeasurementText = 'kWh' AND refRateCode = 'Residential' ")

test1 = test %>%
  mutate(Offer_Date = substring(test$PublishDate, 1, 10)) %>%
  mutate(Offer_Date = ymd(Offer_Date)) %>%
  mutate(ContractTerms = as.factor(ContractTerms)) 

remove(test)

dbDisconnect(conn)

```


This plot shows smoothing curves for each territory, the color indicates the contract length. The black line is the overall average across contracts. 


```{r}

test1 %>%
  filter(Price < 1) %>%
  ggplot(aes(x = Offer_Date, y = Price)) +
  geom_smooth(se = F, aes(color = ContractTerms)) +
  geom_smooth(se = T, method = 'lm',color = 'grey14') +
  facet_wrap(~TerritoryName) +
  xlab("Date") +
  ggtitle("Residential Electric Rates, By Territoy") +
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) 
  

```


```{r, fig.height=10, fig.width=10}

test1 %>%
  filter(Price < 1) %>%
  ggplot(aes(x = Offer_Date, y = Price)) +
  geom_smooth(se = F, method = 'lm', aes(color = SupplierCompanyName), alpha = .4) +
  facet_wrap(~TerritoryName + ContractTerms) +
  geom_smooth(se = T, method = 'lm',color = 'grey14', size = 1.2) +
  xlab("Date") +
  ggtitle("Residential Electric Rates, By Company and Contract Length") +
  ylim(.03, .08) +
  theme_bw() +
  theme(strip.background =element_rect(fill="black")) +
  theme(strip.text = element_text(colour = 'white')) +
  theme(legend.position = "none")


```

The above plot shows lines fit to individual CRES company offers, facetted by territory and contract length. There is hetergeneity in the trends. Some companies do not have many observations. 